Capstone Movielens Report

### 2025-11-24 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report, "UME Model Regulariztion" section  refactoing: extra subsection removed.

#### UME Model Regularization: Support Functions
\

::: {.noteblock data-latex=""}
The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::

##### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function {#func.regularize.test_lambda.UM_effect.cv}
\

This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross-Validation_ method for the given $\lambda$ parameter value:
```{r, eval=FALSE}
regularize.test_lambda.UM_effect.cv <- function(lambda){
  if (is.na(lambda)) {
    stop("Function: regularize.test_lambda.UM_effect.cv
`lambda` is `NA`")
  }
  um_effect <- train_user_movie_effect.cv(lambda)
  calc_user_movie_effect_RMSE.cv(um_effect)
}
```

::: {.noteblock data-latex=""}
Note that we reuse the function [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) calling it from the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
:::

#### UME Model Regularization: Pre-configuration
\

>>>>

#### UME Model Regularization: *Pre-configuration*
\
